### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: apply @dmitromikh suggestions
SYRCoSE: fix grammar

We use the inverse covering function because it is 
more convenient in our setting. Indeed, the semantics adds new event
at each step. Then it is convenient to require that in addition 
the small-step relation is provided with the $\lPO$ and $\lRF$
predecessors of a new event.

@@

The primitive conflict relation is generated by the $\lfPO$ function.
The two events are considered to be in primitive conflict if they are
not equal and have a common $\lPO$ predecessor. 
For this definition to work properly, we also need 
to assume that in each thread has a special initial event 
labelled by a distinguished \emph{thread start} label $\tslab{}$.

>>>>

We use the inverse covering function because it is 
more convenient in our setting. Indeed, the semantics adds a new event
at each step. Then it is convenient to require that in addition 
the small-step relation is provided with the $\lPO$ and $\lRF$
predecessors of a new event.

@@

The primitive conflict relation is generated by the $\lfPO$ function.
The two events are considered to be in primitive conflict if they are
not equal and have a common $\lPO$ predecessor. 
For this definition to work properly, we also need 
to assume that each thread has a special initial event 
labelled by a distinguished \emph{thread start} label $\tslab{}$.
